---
title: "data_preprocessing_normalization+BoxCox"
author: "Lingfeng Huo"
date: "2022/4/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Part II  In this part, we preprocess the train data and test data through BoxCox transformation and z-score normalization

```{r load packages}
library(mlbench)
library(MASS)
library(glmvsd)
library(dplyr)
```  
(1) Read the original train and test data
```{r read data}
trainnew<-read.csv("Autoinsurance_train.csv")
testnew<-read.csv("Autoinsurance_test.csv")
```  
(2) Box-Cox Transformation
Below we consider Box-Cox transformation for the predictors selected. We first plot the log-likelihood functions for each predictor and found the lambda that maximizes the log-likelihood function. Then, the lambda is used as the power to transform the corresponding predictor.  
```{r Transformation by BC}
# The predictors to consider Box-Cox
predr_nm<-c("age_of_driver", "safty_rating", "annual_income", "claim_est_payout", "vehicle_price", "vehicle_weight") 

# plot the log-likelihood functions for each predictor and found the lambda that maximizes the log-likelihood function
for (i in 1:length(predr_nm)) {
  MASS::boxcox(trainnew[,predr_nm[i]]~1)
}

# Result of BC:
# log transformation:
# "age_of_driver"    "claim_est_payout" "vehicle_price"    "vehicle_weight" 

# square transformation:
# "safty_rating"  "annual_income"

# Do the transformation for the trainset and testset
# trainset
trainnew$age_of_driver<-log(trainnew$age_of_driver)
trainnew$claim_est_payout<-log(trainnew$claim_est_payout)
trainnew$vehicle_price<-log(trainnew$vehicle_price)
trainnew$vehicle_weight<-log(trainnew$vehicle_weight)
trainnew$safty_rating<-(trainnew$safty_rating)^2
trainnew$annual_income<-(trainnew$annual_income)^2

# testset
testnew$age_of_driver<-log(testnew$age_of_driver)
testnew$claim_est_payout<-log(testnew$claim_est_payout)
testnew$vehicle_price<-log(testnew$vehicle_price)
testnew$vehicle_weight<-log(testnew$vehicle_weight)
testnew$safty_rating<-(testnew$safty_rating)^2
testnew$annual_income<-(testnew$annual_income)^2
```  

(3) Z-score Normalization for all variables
```{r}
for (i in 1:(ncol(trainnew)-1))
{
  # trainset
  trainnew[,i]<-(trainnew[,i]-mean(trainnew[,i]))/sd(trainnew[,i])
  # testset
  testnew[,i]<-(testnew[,i]-mean(testnew[,i]))/sd(testnew[,i])
}
```  

(4) output the new trainset and testset
```{r output the trainset and testset}
# output the trainset named as Autoinsurance_trainnew.csv
write.csv(trainnew, file=paste0("Autoinsurance_trainnew", ".csv"), row.names=F)
# output the testset named as Autoinsurance_testnew.csv 
write.csv(testnew, file=paste0("Autoinsurance_testnew", ".csv"), row.names=F)
```  

